Crunching Large Graphs with Commodity Processors

### 2011-04-20 doc/hotpar2011/softxmt-hotpar2011.tex
final
author list

\authorinfo{Jacob Nelson$^{\dagger}$, Brandon Myers$^{\dagger}$, A.H. Hunter$^{\dagger}$, Luis
  Ceze$^{\dagger}$,
  Dan Grossman$^{\dagger}$, Mark Oskin$^{\dagger}$, Carl Ebeling$^{\dagger}$, Simon Kahan$^{{\dagger \ddagger}}$, Preston Briggs$^{\dagger}$}{\textdagger University of Washington, \textdaggerdbl Pacific Northwest National Laboratory}{\{nelson, bdmyers, ahh, luisceze, djg, oskin, ebeling, skahan, preston\}@cs.washington.edu}

@@

Any network communication must travel over the QPI link in our test
system. We estimated the bandwidth of this link by allocating lists in
the first chip's memory and traversing those lists on the second
chip's cores. We found that use of the QPI link limits us to
\mrps{175}.

>>>>

\authorinfo{Jacob Nelson$^{\dagger}$,
  Brandon Myers$^{\dagger}$,
  A.H. Hunter$^{\dagger}$,
  Preston Briggs$^{\dagger}$
  Luis Ceze$^{\dagger}$,
  Carl Ebeling$^{\dagger}$,\\
  Dan Grossman$^{\dagger}$,
  Simon Kahan$^{{\dagger \ddagger}}$,
  Mark Oskin$^{\dagger}$,
}{\textdagger University of Washington, \textdaggerdbl Pacific Northwest National Laboratory}{
  \{nelson, bdmyers, ahh, preston, luisceze, ebeling, djg, skahan, oskin\}@cs.washington.edu}

@@

Any network communication must travel over the QPI link in our test
system. We estimated the bandwidth of this link by allocating lists in
the first chip's memory and traversing those lists on the second
chip's cores. We found that use of the QPI link limits throughput to
\mrps{175}.
